---
title: "Assessment1part123.rmd"
author: "Karan"
date: "29/08/2021"
output: html_document
---
```{r}
library(rmarkdown)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## rmarkdown editing 
*Workflow R Markdown is a format for writing reproducible, dynamic reports with R. Use it to. embed R code and results into slideshows, pdfs, html documents, Word files and more*

##karan's page 
image: ! [](C:\Users\karan\Downloads/sydney.jpg)


data<-5
data_text<-“5”
fastfood<-readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv')

library(tidyverse)
library(skimr)
library(janitor)

data<-read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")

data%>%head(10)
knitr::kable(head(fastfood[, 1:5]),"pipe")

fastfood%>% filter(calories>1000)

```{r}
dont_eat_this=fastfood[fastfood$total_fat>40 & fastfood$total_carb>80, ]
dont_eat_this

```


```{r}
library(skimr)
skim(fastfood)

```

```{r}
table(fastfood$restaurant)

```

```{r}
library(dplyr)
fastfood%>% 
  group_by(restaurant) %>% 
  
  summarize(avg = mean(calories))
```


```{r}
library(dplyr)
fastfood=fastfood%>% 
  group_by(restaurant) %>% 
  mutate(average_calories = mean(calories))
fastfood

```


```{r}
library(ggplot2)
barplot(tot_fat$Total_fat,names.arg=tot_fat$restaurant,xlab="Restaurant",ylab="Total_fat",las=2)

```


Visualization of data allows companies to obtain insight into their huge volumes of data. It helps you to discover new data patterns and errors

```{r}
fastfood=fastfood%>% 
  group_by(restaurant) %>% 
  mutate(max_total_fat = max(total_fat))
fastfood

```
```{r}
str(fastfood)
```
```{r}
fastfood$restaurant= as.factor(fastfood$restaurant)
fastfood$salad = as.factor(fastfood$salad)
```


```{r}
fastfood$calories_type=cut_number(fastfood$calories,n=3,c("low","med","high"))

```


```{r}
library(ggplot2)
library(ggpubr)
p=ggscatter(fastfood, x = "restaurant", y = "calories", color = "calories_type",
   palette = c("#0000FF", "#800080", "#C0C0C0"))
p +theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```
```{r}
fastfood$trans_fat_percent= fastfood$trans_fat/fastfood$total_fat
```

```{r}
p=ggscatter(fastfood, x = "restaurant", y = "trans_fat",
   palette = c("#808000", "#00FF00", "#008000"))
p +theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```


```{r}
avg_fat=fastfood%>% 
  group_by(restaurant) %>% 
  
  summarize(Total_fat = mean(total_fat))
avg_fat

```
```{r}
library(ggplot2)
barplot(avg_fat$Total_fat,names.arg=avg_fat$restaurant,xlab="Restaurant",ylab="Total_fat",las=3)
```






